---
title: "My Final Project Presentation"
author: Weishan Bai
subtitle: Correlation analysis between population changing and housing changing——Taking New York City as an example
---

# Introduction
With the development of economy and urbanization, the dramatic changes of urban population have accelerated. This phenomenon is more common in megalopolises. People may move to cities for job opportunities or stay away from cities for better quality of life. At the same time as the population is changing, the house will switch between occupied and vacant. Meanwhile, housing prices will also be affected. In this research, we take the metropolitan area that New York City as an example, and show the plot and form of the changes in population, number of housing, housing value and household income in New York City. In addition, the method of regression analysis is used to explore the correlation between these variables. This study will propose three hypotheses: 1) The amount of urban population change is negatively related to the number of vacant houses;2) The value of the house is positively correlated with the income of the household; 3) The amount of change in urban population is positively correlated with house value. In order to verify the hypothesis, this study will use American Community Survey (ACS) Data from 2013-2018.


# Materials and methods

[~ 200 words]

Narrative: Clear narrative description of the data sources and methods. Includes data from at least two sources that were integrated / merged in R.

Code: The code associated with the project is well organized and easy to follow. Demonstrates mastery of R graphics and functions.

Data: The underlying data are publicly accessible via the web and downloaded/accessed within the Rmd script. If you want to use your own data, you must make it available on a website (e.g. Figshare) so that others are able to re-run your code.

You can do bullets like this:

* The first most important thing
* The second most important thing
* The third most important thing

You can do numbers like this:

1. The first most important thing
2. The second most important thing
3. The third most important thing

See [http://rmarkdown.rstudio.com/](http://rmarkdown.rstudio.com/) for all the amazing things you can do.

Load any required packages in a code chunk (you may need to install some packages):

```{r, message=F, warning=F}
library(tidyverse)
library(leaflet)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(corrplot)
library(cowplot)
knitr::opts_chunk$set(cache=TRUE)  # cache the results for quick compiling
```

## Read and summary data
```{r}
options(scipen = 200)
datapath="./Dataset/NYC.csv"
nyc=read.csv(datapath)
nyc_whole<-nyc%>%filter(Area=="New York City")
each_county<-nyc%>%filter(Area!="New York City")
```

```{r, results='asis'}
nyc %>% 
  slice(1:10) %>% #show only 1:n rows
  kable(digits=2,align="c")%>% #make table and round to two digits
  kable_styling(bootstrap_options = 
                  c("striped", "hover", "condensed", "responsive")) #apply other formatting
```

# Visualization and analysis of the data

## First hypothesis


The change of the number of vacant housing and the household income of NYC
```{r, results='asis',out.width = "1526", out.height = "428"}
p1<-nyc_whole%>%
  ggplot(aes(x=Year,y=Total_population,group=Area))+geom_line(size=1,color=2)+geom_point(size=3,color=4)+ylab('Population')+labs(title = 'The change of population')+
  theme(plot.title = element_text(hjust = 0.5))
p2<-nyc_whole%>%
  ggplot(aes(x=Year,y=Vacant_housing,group=Area))+geom_line(size=1,color=3)+geom_point(size=3,color=5)+ylab('The number of vacant housing')+labs(title = 'The change of  vacant housing')+
  theme(plot.title = element_text(hjust = 0.5))
plot_grid(p1, p2)

```

The change of population and number of vacant housing of each county
```{r, results='asis',out.width = "1526", out.height = "728"}
p3<-each_county%>%
  ggplot(aes(x=Year,y=Total_population,group=Area))+geom_line(size=1,color=2)+geom_point(size=3,color=4)+ylab('Population')+labs(title = 'The change of \n population in each county')+facet_wrap(~Area,scales="free_y",nrow=5,as.table = TRUE)+
  theme(plot.title = element_text(hjust = 0.5))
p4<-each_county%>%ggplot(aes(x=Year,y=Vacant_housing,group=Area))+geom_line(size=1,color=3)+geom_point(size=3,color=5)+ylab('The number of vacant housing')+labs(title = 'The change of \n vacant housing in each county')+facet_wrap(~Area,scales="free_y",nrow=5,as.table = TRUE)+
  theme(plot.title = element_text(hjust = 0.5))
plot_grid(p3, p4)

```

## Second hypothesis
The change of median housing value and median household income of NYC
```{r, results='asis',out.width = "1526", out.height = "428"}
p5<-nyc_whole%>%
  ggplot(aes(x=Year,y=Median_value,group=Area))+geom_line(size=1,color=2)+geom_point(size=3,color=4)+ylab('Median value(dollors)')+labs(title = 'The change of \n median value of housing')+
  theme(plot.title = element_text(hjust = 0.5))
p6<-nyc_whole%>%
  ggplot(aes(x=Year,y=Median_income,group=Area))+geom_line(size=1,color=3)+geom_point(size=3,color=5)+ylab('Median household income(dollors)')+labs(title = 'The change of \n  median household income')+
  theme(plot.title = element_text(hjust = 0.5))
plot_grid(p5, p6)

```

The change of median housing value and median household income of each county
```{r, results='asis',out.width = "1526", out.height = "728"}
p7<-each_county%>%
  ggplot(aes(x=Year,y=Median_value,group=Area))+geom_line(size=1,color=2)+geom_point(size=3,color=4)+ylab('Population')+labs(title = 'The change of  median \n housing value in each county')+facet_wrap(~Area,scales="free_y",nrow=5,as.table = TRUE)+
  theme(plot.title = element_text(hjust = 0.5))
p8<-each_county%>%ggplot(aes(x=Year,y=Median_income,group=Area))+geom_line(size=1,color=3)+geom_point(size=3,color=5)+ylab('The number of vacant housing')+labs(title = 'The change of  median \n household income in each county')+facet_wrap(~Area,scales="free_y",nrow=5,as.table = TRUE)+
  theme(plot.title = element_text(hjust = 0.5))
plot_grid(p7, p8)

```


## The third hypothesis
The change of population and median housing value of NYC
```{r, results='asis',out.width = "1526", out.height = "428"}
p9<-nyc_whole%>%
  ggplot(aes(x=Year,y=Total_population,group=Area))+geom_line(size=1,color=2)+geom_point(size=3,color=4)+ylab('Median value(dollors)')+labs(title = 'The change of \n population')+
  theme(plot.title = element_text(hjust = 0.5))
p10<-nyc_whole%>%
  ggplot(aes(x=Year,y=Median_value,group=Area))+geom_line(size=1,color=3)+geom_point(size=3,color=5)+ylab('Median value(dollors)')+labs(title = 'The change of \n median value of housing')+
  theme(plot.title = element_text(hjust = 0.5))
plot_grid(p9, p10)

```

The change of population and median housing value of each county
```{r, results='asis',out.width = "1526", out.height = "728"}
p11<-each_county%>%
  ggplot(aes(x=Year,y=Total_population,group=Area))+geom_line(size=1,color=2)+geom_point(size=3,color=4)+ylab('Population')+labs(title = 'The change of \n population in each county')+facet_wrap(~Area,scales="free_y",nrow=5,as.table = TRUE)+
  theme(plot.title = element_text(hjust = 0.5))
p12<-each_county%>%ggplot(aes(x=Year,y=Median_value,group=Area))+geom_line(size=1,color=3)+geom_point(size=3,color=5)+ylab('Median value(dollors)')+labs(title = 'The change of median value \n of housing in each county')+facet_wrap(~Area,scales="free_y",nrow=5,as.table = TRUE)+
  theme(plot.title = element_text(hjust = 0.5))
plot_grid(p11, p12)

```

The result of Pearson Correlation Coefficient
```{r, results='asis',include=FALSE}
nyc_pop<-nyc_whole[,"Total_population"]
nyc_vh<-nyc_whole[,"Vacant_housing"]
nyc_value<-nyc_whole[,"Median_value"]
nyc_income<-nyc_whole[,"Median_income"]
bx<-each_county%>%filter(Area=='Bronx')
bx_pop<-bx[,"Total_population"]
bx_vh<-bx[,"Vacant_housing"]
bx_value<-bx[,"Median_value"]
bx_income<-bx[,"Median_income"]
bn<-each_county%>%filter(Area=='Brooklyn')
bn_pop<-bn[,"Total_population"]
bn_vh<-bn[,"Vacant_housing"]
bn_value<-bn[,"Median_value"]
bn_income<-bn[,"Median_income"]
bn<-each_county%>%filter(Area=='Brooklyn')
bn_pop<-bn[,"Total_population"]
bn_vh<-bn[,"Vacant_housing"]
bn_value<-bn[,"Median_value"]
bn_income<-bn[,"Median_income"]
mh<-each_county%>%filter(Area=='Manhattan')
mh_pop<-mh[,"Total_population"]
mh_vh<-mh[,"Vacant_housing"]
mh_value<-mh[,"Median_value"]
mh_income<-mh[,"Median_income"]
q<-each_county%>%filter(Area=='Queens')
q_pop<-q[,"Total_population"]
q_vh<-q[,"Vacant_housing"]
q_value<-q[,"Median_value"]
q_income<-q[,"Median_income"]
si<-each_county%>%filter(Area=='Staten Island')
si_pop<-si[,"Total_population"]
si_vh<-si[,"Vacant_housing"]
si_value<-si[,"Median_value"]
si_income<-si[,"Median_income"]

# for whole nyc
nyc_pop_vacant<-cor(x=nyc_pop,y=nyc_vh)
nyc_value_income<-cor(x=nyc_value,y=nyc_income)
nyc_pop_value<-cor(x=nyc_pop,y=nyc_value)
#for Bronx
bx_pop_vacant<-cor(x=bx_pop,y=bx_vh)
bx_value_income<-cor(x=bx_value,y=bx_income)
bx_pop_value<-cor(x=bx_pop,y=bx_value)
#for Brooklyn
bn_pop_vacant<-cor(x=bn_pop,y=bn_vh)
bn_value_income<-cor(x=bn_value,y=bn_income)
bn_pop_value<-cor(x=bn_pop,y=bn_value)
#for Manhattan
mh_pop_vacant<-cor(x=mh_pop,y=mh_vh)
mh_value_income<-cor(x=mh_value,y=mh_income)
mh_pop_value<-cor(x=mh_pop,y=mh_value)
#for Queens
q_pop_vacant<-cor(x=q_pop,y=q_vh)
q_value_income<-cor(x=q_value,y=q_income)
q_pop_value<-cor(x=q_pop,y=q_value)
# for Staten Island
si_pop_vacant<-cor(x=si_pop,y=q_vh)
si_value_income<-cor(x=si_value,y=q_income)
si_pop_value<-cor(x=si_pop,y=q_value)


```



# Results

[~200 words]

Tables and figures (maps and other graphics) are carefully planned to convey the results of your analysis. Intense exploration and evidence of many trials and failures. The author looked at the data in many different ways before coming to the final presentation of the data.

Show tables, plots, etc. and describe them.

```{r, fig.width=6, fig.height=3, fig.cap="Map of completely random data"}

```


```{r, results='asis'}
population_vacant<-data.frame('Area'=c("New York City","Bronx","Brooklyn","Manhattan","Queens","Staten Island"),'Pearson correlation coefficient'=c(nyc_value_income,bx_value_income,bn_value_income,mh_value_income,q_value_income,si_value_income))
population_vacant%>%kable(digits=2,align="c",caption = "The pearson correlation cofficient between total of population and the number of vacant housing",font_size = 17)%>% 
  kable_styling(bootstrap_options = 
                  c("striped", "hover", "condensed", "responsive"))
```
```{r, results='asis'}
value_income<-data.frame('Area'=c("New York City","Bronx","Brooklyn","Manhattan","Queens","Staten Island"),'Pearson correlation coefficient'=c(nyc_pop_vacant,bx_pop_vacant,bn_pop_vacant,mh_pop_vacant,q_pop_vacant,si_pop_vacant))
population_vacant%>%kable(digits=2,align="c",caption = "The pearson correlation cofficient between total of population and the number of vacant housing",font_size = 17)%>% 
  kable_styling(bootstrap_options = 
                  c("striped", "hover", "condensed", "responsive"))
```

```{r, results='asis'}
pop_value<-data.frame('Area'=c("New York City","Bronx","Brooklyn","Manhattan","Queens","Staten Island"),'Pearson correlation coefficient'=c(nyc_pop_value,bx_pop_value,bn_pop_value,mh_pop_value,q_pop_value,si_pop_value))
population_vacant%>%kable(digits=2,align="c",caption = "The pearson correlation cofficient between total of population and the number of vacant housing",font_size = 17)%>% 
  kable_styling(bootstrap_options = 
                  c("striped", "hover", "condensed", "responsive"))
```

# Conclusions

[~200 words]

Clear summary adequately describing the results and putting them in context. Discussion of further questions and ways to continue investigation.

# References

All sources are cited in a consistent manner
