---
title: "My Final Project Presentation"
author: Weishan Bai
subtitle: Subtitle here if desired
---

# Introduction
With the development of economy and urbanization, the dramatic changes of urban population have accelerated. This phenomenon is more common in megalopolises. People may move to cities for job opportunities or stay away from cities for better quality of life. At the same time as the population is changing, the house will switch between occupied and vacant. Meanwhile, housing prices will also be affected. In this research, we take the metropolitan area that New York City as an example, and show the plot and form of the changes in population, number of housing, housing value and household income in New York City. In addition, the method of regression analysis is used to explore the correlation between these variables. This study will propose three hypotheses: 1) The amount of urban population change is negatively related to the number of vacant houses;2) The value of the house is positively correlated with the income of the household; 3) The amount of change in urban population is positively correlated with house value. In order to verify the hypothesis, this study will use American Community Survey (ACS) Data from 2013-2018.


# Materials and methods

[~ 200 words]

Narrative: Clear narrative description of the data sources and methods. Includes data from at least two sources that were integrated / merged in R.

Code: The code associated with the project is well organized and easy to follow. Demonstrates mastery of R graphics and functions.

Data: The underlying data are publicly accessible via the web and downloaded/accessed within the Rmd script. If you want to use your own data, you must make it available on a website (e.g. Figshare) so that others are able to re-run your code.

You can do bullets like this:

* The first most important thing
* The second most important thing
* The third most important thing

You can do numbers like this:

1. The first most important thing
2. The second most important thing
3. The third most important thing

See [http://rmarkdown.rstudio.com/](http://rmarkdown.rstudio.com/) for all the amazing things you can do.


Here's my first code chunk.
```{r}
1+2
```

Load any required packages in a code chunk (you may need to install some packages):

```{r, message=F, warning=F}
library(tidyverse)
library(leaflet)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(corrplot)
knitr::opts_chunk$set(cache=TRUE)  # cache the results for quick compiling
```

## Read and summary data
```{r}
datapath="./Dataset/NYC.csv"
nyc=read.csv(datapath)
mode(nyc[,"Total_population"])
```

```{r, results='asis'}
nyc %>% 
  slice(1:10) %>% #show only 1:n rows
  kable(digits=2,align="c")%>% #make table and round to two digits
  kable_styling(bootstrap_options = 
                  c("striped", "hover", "condensed", "responsive")) #apply other formatting
```

# Processing and plot the data
The change of population of NYC
```{r, results='asis'}

nyc_population<-nyc%>%filter(Area=="New York City")
p1<-nyc_population%>%
  ggplot()+geom_line(data = nyc_population,aes(x = Year,y = Total_population,group=1,colour = "Population"),size=1)+
  geom_point(data = nyc_population,aes(x = Year,y = Total_population,group=1,colour = "Population"),size=3)+
  geom_line(data = nyc_population,aes(x = Year,y = Vacant_housing,group=1,colour ="The number of Vacant housing"),size=1) + 
  geom_point(data = nyc_population,aes(x = Year,y = Vacant_housing,group=1,colour = "The number of Vacant housing"),size=3)+
  scale_colour_manual("",values = c("Population" = "red","The number of Vacant housing" = "green"))+
  xlab("Year")+ylab("Amount")
  
p1
```
The change of population of each county


```{r, results='asis'}
no_nyc<-nyc%>%filter(Area!="New York City")

p2<-ggplot()+geom_line(data = no_nyc,aes(x = Year,y = Total_population,group=Area,colour = "Population"),size=1)+
  geom_point(data = no_nyc,aes(x = Year,y = Total_population,group=Area,colour = "Population"),size=3)+
  geom_line(data = no_nyc,aes(x = Year,y = Vacant_housing,group=Area,colour ="The number of Vacant housing"),size=1) + 
  geom_point(data = no_nyc,aes(x = Year,y = Vacant_housing,group=Area,colour = "The number of Vacant housing"),size=3)+scale_y_discrete(breaks=NULL)+
  scale_colour_manual("",values = c("Population" = "red","The number of Vacant housing" = "green"))+
  xlab("Year")+ylab("Amount")+facet_wrap(~Area,scales="free_y",nrow=3,as.table = FALSE)
p2
```

```{r, results='asis'}
datapath1="./Dataset/NYC1.csv"
nyc_cor=read.csv(datapath1)
res_cor<-cor(x=nyc_cor[,"Total_population"],y=nyc_cor[,"Vacant_housing"])
res_cor
```

# Results

[~200 words]

Tables and figures (maps and other graphics) are carefully planned to convey the results of your analysis. Intense exploration and evidence of many trials and failures. The author looked at the data in many different ways before coming to the final presentation of the data.

Show tables, plots, etc. and describe them.

```{r, fig.width=6, fig.height=3, fig.cap="Map of completely random data"}

```


```{r}

```

# Conclusions

[~200 words]

Clear summary adequately describing the results and putting them in context. Discussion of further questions and ways to continue investigation.

# References

All sources are cited in a consistent manner
